NumPy---Array Programming in Python

### 2020-02-15 body.tex
Two minor fixes

NumPy's is no longer \emph{just} the foundational array library underlying
the scientific Python ecosystem, but has also become the standard API
for tensor computation and a central coordinating mechanism between
array types and technologies in Python. Work continues to expand on and
improve these interoperability features.

Over the next decade, we will face several new challenges.
%Artificial
%Intelligence and Data Science will mature ... [what do we say about
%  this?].
New devices will be developed, and existing specialized
hardware will evolve, to meet diminishing returns on Moore's law.
There will be more, and a wider variety of, data science
practitioners, a significant proportion of whom will be using NumPy.
The scale of scientific data gathering will continue to expand, with
the adoption of devices and instruments such as light sheet
microscopes and the LSST \cite{jenness2018lsst}.  New generation languages, interpreters, and compilers,
such as Rust \cite{10.1145/2692956.2663188}, Julia \cite{Julia-2017}, and LLVM \cite{LLVM:CGO04}, will invent
and determine the viability of new concepts and data structures.

>>>>

NumPy is no longer \emph{just} the foundational array library underlying
the scientific Python ecosystem, but has also become the standard API
for tensor computation and a central coordinating mechanism between
array types and technologies in Python. Work continues to expand on and
improve these interoperability features.

Over the next decade, we will face several new challenges.
%Artificial
%Intelligence and Data Science will mature ... [what do we say about
%  this?].
New devices will be developed, and existing specialized
hardware will evolve, to meet diminishing returns on Moore's law.
There will be more, and a wider variety of, data science
practitioners, a significant proportion of whom will be using NumPy.
The scale of scientific data gathering will continue to expand, with
the adoption of devices and instruments such as light sheet
microscopes and the Large Synoptic Survey Telescope (LSST) \cite{jenness2018lsst}.  New generation languages, interpreters, and compilers,
such as Rust \cite{10.1145/2692956.2663188}, Julia \cite{Julia-2017}, and LLVM \cite{LLVM:CGO04}, will invent
and determine the viability of new concepts and data structures.
